Probabilistic Inference of Basic Stellar Parameters:\\ Application to Flickering Stars \altaffilmark{\titledag}

### 2016-02-25 version1.0/manuscript.tex
starting to add referee comments

We used a likelihood function which accounts for 2-D uncertainties but does
not allow the intrinsic scatter to be a function of the dependent or
independent variables.
For the relation between flicker and \rhostar, this likelihood function can be
written as
\begin{eqnarray}
	& p(F_8|\rho_\star, \alpha_\rho, \beta_\rho, \sigma_{\rho}) \propto  \\ \nonumber
						      & \exp \left[-\frac{1}{2}
		\sum_{n=1}^N \frac{[F_{8n}-(\alpha_\rho + \beta_\rho \rho_{*n})]^2}
	{\left[\beta_\rho \sigma_{F8, n}^2 + \sigma_{\rho *, n}^2
	+ \sigma_{\rho}^2\right]}\right]
	\\ \nonumber
	& + \beta_\rho^2 \sigma_{F8, n}^2 + \sigma_{\rho *, n}^2 + \sigma_{\rho}^2,
\end{eqnarray}
\label{eq:likelihood}
and similarly for \logg.
We found that the posterior PDFs for the model parameters obtained using this
likelihood function were consistent with those obtained using a model that
only accounts for the uncertainties on the flicker measurements.
Accounting for uncertainties on $y$ {\it and} $x$ is therefore not essential
in this case but still good practise and will, in general, produce more
accurate model parameters and uncertainties.

% so instead
% used a standard Gaussian likelihood function $(-1/2\chi^2)$ in our analysis.
% Since the uncertainties on flicker were significantly larger than those on
% \logg or \rhostar, regression was performed with flicker as the dependent
% variable.

@@

We also tested flat priors and found that the results were insensitive to this
choice.
Figures \ref{fig:rhostar} and \ref{fig:logg} show the data with the best-fit
models.
The shaded regions show the 1 and 2$\sigma$ confidence interval which are
representative of the intrinsic scatter in the relations.
% Given a measurement of flicker, the predictive probability distribution of
% \logg and \rhostar will be a Gaussian distribution

@@

@@

RA would like to thank Dan Foreman-Mackey for his extremely helpful suggestions
and comments, Angie Wolfgang for her expert guidance and John Johnson for hit
fantastic advice and support.
RA would also like to thank the SAMSI institute and the other members of the
SAMSI {\it Kepler} exoplanet statistics working groups.

@@

% #####################################################################
%% Bibliography
\begin{thebibliography}{99}
\bibitem[\protect\citeauthoryear{Andrieu \& Roberts}{2009}]{andrieu:2009}
Andrieu, C., \& Roberts, G.~O., Ann. Statist., 2, 695
\bibitem[\protect\citeauthoryear{Angus et al.}{2015}]{angus:2015}
Angusr, R., Aigrain, S., Foreman-Mackey, D. \& McQuillan, A., 2015, MNRAS,
450, 1787
\bibitem[\protect\citeauthoryear{Bastien et al.}{2013}]{bastien:2013} Bastien,
F. A., Stassun, K. G., Basri, G. \& Pepper, J., 2013, Nature, 500, 427
\bibitem[\protect\citeauthoryear{Chaplin et al.}{2014}]{chaplin:2014}
Chaplin, W.~J., Basu, S., Huber, D. et al., 2014, ApJS, 210, 1
\bibitem[\protect\citeauthoryear{Cranmer et al.}{2014}]{cranmer:2014}
Cranmer, S. R., Bastien, F. A., Stassun, K. G. \& Saar, S. H., 2014, ApJ, 781,
124
\bibitem[\protect\citeauthoryear{Foreman-Mackey et al.}{2014}]
{foreman-mackey:2014} Foreman-Mackey, D., Hogg, D.~W. \& Morton, T.~D., 2014,
ApJ, 795, 64
\bibitem[Foreman-Mackey et al.(2013)]{foreman-mackey:2013}
Foreman-Mackey, D., Hogg, D.~W., Lang, D., \& Goodman, J.\ 2013, \pasp, 125, 306
\bibitem[\protect\citeauthoryear{Fox}{1997}]{fox:1997}
Fox, J., 1997, Applied Regression Analysis, Linear Models, and Related Methods
(Thousand Oaks:Sage Publications, Inc.)
\bibitem[\protect\citeauthoryear{Fuller}{1987}]{fuller:1987}
Fuller, W.~A., 1987, Wiley Series in Probability and Mathematical Statistics
\bibitem[\protect\citeauthoryear{Hogg et al.}{2010}]{hogg:2010}
Hogg, D.~W., Myers, A.~D. \& Bovy, J., 2010, ApJ, 725,
2166
\bibitem[\protect\citeauthoryear{Hogg et al.}{2010b}]{hogg:2010b}
Hogg, D.~W., Bovy, J. \& Lang, D., 2010
\bibitem[\protect\citeauthoryear{Huber et al.}{2013}]{huber:2013}
Huber, D., Chaplin, W.~J., Christensen-Dalsgaard, J. et al., 2013, ApJ, 767,
127
\bibitem[\protect\citeauthoryear{Kelly}{2007}]{kelly:2007} Kelly, B.~C., 2007,
ApJ, 665, 1489
\bibitem[\protect\citeauthoryear{Kipping et al.}{2014}]{kipping:2014}
Kipping, D.~M., Bastien, F.~A., Stassun, K.~G., Chaplin, W.~J., Huber, D. \&
Buchhave, L.~A., 2014, ApJ, 785, 32
\bibitem[\protect\citeauthoryear{Rogers}{2015}]{rogers:2015}
Rogers, L.~A., 2015, ApJ, 801, 41
\bibitem[\protect\citeauthoryear{Seager \& Mall\'{e}n-Ornelas}{2003}]
{seager:2003}Seager, S., \& Mall\'{e}n-Ornelas, G., 2003, ApJ, 585, 1038
\bibitem[VanderPlas(2014)]{vanderplas}
VanderPlas, J.\ 2014, arXiv:1411.5018
\bibitem[\protect\citeauthoryear{Wolfgang et al.}{2015}]{wolfgang:2015}
Wolfgang, A., Rogers, L.~A., Ford, E.~B., 2015, ApJ, submitted
(astro-ph:1504.07557)
\end{thebibliography}

>>>>

We used a likelihood function which accounts for 2-D uncertainties but does
not allow the intrinsic scatter to be a function of the dependent or
independent variables.
For the relation between flicker and \rhostar, this likelihood function can be
written as
\begin{eqnarray}
	& p(F_8|\rho_\star, \alpha_\rho, \beta_\rho, \sigma_{\rho}) \propto  \\ \nonumber
						      & \exp \left[-\frac{1}{2}
		\sum_{n=1}^N \frac{[F_{8n}-(\alpha_\rho + \beta_\rho \rho_{*n})]^2}
	{\left[\beta_\rho \sigma_{F8, n}^2 + \sigma_{\rho *, n}^2
	+ \sigma_{\rho}^2\right]}\right]
	\\ \nonumber
	& + \beta_\rho^2 \sigma_{F8, n}^2 + \sigma_{\rho *, n}^2 + \sigma_{\rho}^2,
\end{eqnarray}
\label{eq:likelihood}
and similarly for \logg.
We found that the posterior PDFs for the model parameters obtained using this
likelihood function were consistent with those obtained using a model that
only accounts for the uncertainties on the flicker measurements.
The median values of the model parameters differed by around $0.05 \sigma$
for the $\alpha$ and $\beta$ parameters, by $0.3 \sigma$ for $\sigma_\rho$
and by 0.8 $\sigma$ for $\sigma_g$.
Since they are so dependent on the observational uncertainties, the parameters
that describe the intrinsic scatter in the relations are more sensitive to
whether the uncertainties in the $x$-direction are included.
Accounting for uncertainties on $y$ {\it and} $x$ is not essential in this
case but is still good practise and will, in general, produce more accurate
model parameters and uncertainties.

% Since the uncertainties on flicker were significantly larger than those on
% \logg or \rhostar, regression was performed with flicker as the dependent
% variable.

@@

We also tested uniform, flat priors as defined below:
\begin{eqnarray}
 	&	\alpha, \beta \sim U(-10:10) \\ \nonumber
  	&	\log (\sigma_{rho}), \log(\sigma_g) \sim U(-10:10).
 \end{eqnarray}
 \label{eq:priors}
We found that the results were relatively insensitive to the choice of prior,
with median parameter values differing by only around $0.05\sigma$.
MCMC chains were run until the Gelman \& Rubin convergence criterion,
$\hat{R}$ reached a value of less than 1.002 and the number of autocorrelation
times was greater than 35.
Figures \ref{fig:rhostar} and \ref{fig:logg} show the data with the best-fit
models.
The shaded regions show the 1 and 2$\sigma$ confidence interval which are
representative of the intrinsic scatter in the relations.
The marginal posterior PDFs of the model parameters for \rhostar are shown in
figure \ref{fig:triangle}.
The marginal posterior PDFs for \logg are similarly Gaussian and, as with
$\sigma_\rho$, $\sigma_g$ is clearly greater than zero.

@@

\begin{figure}
\begin{center}
\includegraphics[width=8.4cm,angle=0,clip=true]{rho_triangle.pdf}
\caption{Marginal posterior PDFs of the model parameters for \rhostar.
This figure was generated using the {\tt corner} python package
\citep{corner}.}
\label{fig:triangle}
\end{center}
\end{figure}

@@

RA would like to thank Dan Foreman-Mackey for his extremely helpful suggestions
and comments, Angie Wolfgang for her expert guidance and John Johnson for his
fantastic advice and support.
RA would also like to thank the anonymous referee for their excellent
suggestions, SAMSI institute and the other members of the SAMSI {\it Kepler}
exoplanet statistics working groups.

@@

% #####################################################################
%% Bibliography
\begin{thebibliography}{99}
\bibitem[\protect\citeauthoryear{Andrieu \& Roberts}{2009}]{andrieu:2009}
Andrieu, C., \& Roberts, G.~O., Ann. Statist., 2, 695
\bibitem[\protect\citeauthoryear{Angus et al.}{2015}]{angus:2015}
Angusr, R., Aigrain, S., Foreman-Mackey, D. \& McQuillan, A., 2015, MNRAS,
450, 1787
\bibitem[\protect\citeauthoryear{Bastien et al.}{2013}]{bastien:2013} Bastien,
F. A., Stassun, K. G., Basri, G. \& Pepper, J., 2013, Nature, 500, 427
\bibitem[\protect\citeauthoryear{Chaplin et al.}{2014}]{chaplin:2014}
Chaplin, W.~J., Basu, S., Huber, D. et al., 2014, ApJS, 210, 1
\bibitem[\protect\citeauthoryear{Cranmer et al.}{2014}]{cranmer:2014}
Cranmer, S. R., Bastien, F. A., Stassun, K. G. \& Saar, S. H., 2014, ApJ, 781,
124
\bibitem[\protect\citeauthoryear{Foreman-Mackey et al.}{2014}]
{foreman-mackey:2014} Foreman-Mackey, D., Hogg, D.~W. \& Morton, T.~D., 2014,
ApJ, 795, 64
\bibitem[Foreman-Mackey et al.(2013)]{foreman-mackey:2013}
Foreman-Mackey, D., Hogg, D.~W., Lang, D., \& Goodman, J.\ 2013, \pasp, 125, 306
\bibitem[Foreman-Mackey et al. (2014)]{corner}
Foreman-Mackey, D., Price-Whelan, A., Ryan, G. et al.\ 2014,
10.5281/zenodo.10598, http://dx.doi.org/10.5281/zenodo.10598
\bibitem[\protect\citeauthoryear{Fox}{1997}]{fox:1997}
Fox, J., 1997, Applied Regression Analysis, Linear Models, and Related Methods
(Thousand Oaks:Sage Publications, Inc.)
\bibitem[\protect\citeauthoryear{Fuller}{1987}]{fuller:1987}
Fuller, W.~A., 1987, Wiley Series in Probability and Mathematical Statistics
\bibitem[\protect\citeauthoryear{Hogg et al.}{2010}]{hogg:2010}
Hogg, D.~W., Myers, A.~D. \& Bovy, J., 2010, ApJ, 725,
2166
\bibitem[\protect\citeauthoryear{Hogg et al.}{2010b}]{hogg:2010b}
Hogg, D.~W., Bovy, J. \& Lang, D., 2010
\bibitem[\protect\citeauthoryear{Huber et al.}{2013}]{huber:2013}
Huber, D., Chaplin, W.~J., Christensen-Dalsgaard, J. et al., 2013, ApJ, 767,
127
\bibitem[\protect\citeauthoryear{Kelly}{2007}]{kelly:2007} Kelly, B.~C., 2007,
ApJ, 665, 1489
\bibitem[\protect\citeauthoryear{Kipping et al.}{2014}]{kipping:2014}
Kipping, D.~M., Bastien, F.~A., Stassun, K.~G., Chaplin, W.~J., Huber, D. \&
Buchhave, L.~A., 2014, ApJ, 785, 32
\bibitem[\protect\citeauthoryear{Rogers}{2015}]{rogers:2015}
Rogers, L.~A., 2015, ApJ, 801, 41
\bibitem[\protect\citeauthoryear{Seager \& Mall\'{e}n-Ornelas}{2003}]
{seager:2003}Seager, S., \& Mall\'{e}n-Ornelas, G., 2003, ApJ, 585, 1038
\bibitem[VanderPlas(2014)]{vanderplas}
VanderPlas, J.\ 2014, arXiv:1411.5018
\bibitem[\protect\citeauthoryear{Wolfgang et al.}{2015}]{wolfgang:2015}
Wolfgang, A., Rogers, L.~A., Ford, E.~B., 2015, ApJ, submitted
(astro-ph:1504.07557)
\end{thebibliography}
